Review stages

### 2024-04-05 doc/review-stages.qmd
wip: updates to doc based on meeting

@@

@@

```{r tbl-titles-kept}
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
title_reviews |> 
  map(\(df) count(df, name = "Articles kept")) |> 
  list_rbind(names_to = "Reviewers") |> 
  knitr::kable()
```

```{r tbl-titles-agreements}
#| tbl-cap: "Agreements in article titles kept between all reviewers during the title screening stage."
common_titles <- title_reviews |>
  reduce(\(df1, df2) inner_join(df1, df2, by = join_by(id, title, publication_date, doi)))
common_titles |> 
  select("Article title" = title) |> 
  knitr::kable()
```

@@

>>>>

<!-- TODO: Include last date the articles were extracted from. -->

@@

During the first stage of the reviewing, we only looked at titles. Below
is the code to extract the titles we each individually reviewed, so we
can show some details about how many were included, excluded, and which
titles we agreed on or disagreed on.

@@

In the title screening stage, the number of titles we kept are listed in
@tbl-titles-kept.

```{r tbl-titles-kept}
#| tbl-cap: "Number of articles each reviewer kept after the first screening of the titles."
title_reviews |>
  map(\(df) count(df, name = "Articles kept")) |>
  list_rbind(names_to = "Reviewers") |>
  # TODO: Include percent of total articles.
  knitr::kable()
```

We want to know how many of these titles we all agreed on between the
three reviewers, which is shown in @tbl-titles-agreements

```{r}
common_titles <- title_reviews |>
  reduce(\(df1, df2) {
    inner_join(df1, df2, by = join_by(id, title, publication_date, doi))
  })
```

```{r tbl-titles-agreements}
#| tbl-cap: !expr glue::glue("The {nrow(common_titles)} article titles we all agreed on and kept during the title screening stage.")
common_titles |>
  select("Article title" = title) |>
  knitr::kable()
```

One person will review and flag any o might be relevant but are not in
agreement to keep.

@@

## Abstract review stage

## Reading stage

-   first us reading a few to get an idea of themes and information to
    extract
-   and then discuss together the themes to group by and information to
    extract
-   Then we follow what we agreed on

## Writing stage

-   How to visualize?
